---
title: "visualization"
author: "Qiuyi Lu"
date: "12/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(tidyverse)
install.packages("gplots")
library(gplots)
library(RColorBrewer)
library(reshape2)
library(ggmap)
```
### Heat Map: 
#### We can use heat map to see correlations among variables.<br> It's useful for selecting features when building models. For linear regression model, it can also help check multicollinearity. <br> Many bio companies use heat map to see the gene similarity among different species and could cluster species.

```{r message = F, warning = F}
data=as.matrix(mtcars)

correlation <- cor(data)
fm <- format(round(correlation, 2))

color =colorRampPalette(c("yellow1","yellow2","goldenrod"))

heatmap.2(correlation,
trace="none",# not show trace average line.
col=color,
density.info = "none",
key.xlab ='Correlation',
key.title = "",
cexRow = 1,cexCol = 1,
Rowv = F,Colv = F, #no cluster
margins = c(6, 6),
cellnote = fm,notecol='black'#can use pvalue
            )
# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
  
upper_tri <- get_upper_tri(correlation)
upper_tri
melted_cormat <- melt(upper_tri, na.rm = TRUE) # gather


ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "lightblue", high = "orangered", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()
# Print the heatmap
print(ggheatmap)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}


# Reorder the correlation matrix
cormat <- reorder_cormat(correlation)
upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)
# Create a ggheatmap
ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "skyblue", high = "orangered", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()
# Print the heatmap
print(ggheatmap)

ggheatmap + 
geom_text(aes(Var2, Var1, label = round(value,2)), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(0.6, 0.7),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))

```

### Geographic map

#### We can use map to find the popularity of some places. If we want to set a new station, we can check where do people take a lot of activities and set points there. Rideshare companies can use it to better allocate their drivers and pricing. Travelling/local service companies can recommend the place for users.

```{r message = F, warning = F}
citibike <- readRDS('data/201508.rds') 

station.info <- citibike %>%
  group_by(start.station.id) %>%
  summarise(lat=as.numeric(start.station.latitude[1]),
            long=as.numeric(start.station.longitude[1]),
            name=start.station.name[1],
            n.trips=n())

myKey <- 'AIzaSyBmNOtmsL495gnmU6IlOVNIzNS9fASiNOc'
register_google(key = myKey, account_type = "premium", day_limit = 100000)

newyork.map=get_map(location='Lower Manhattan,New York',maptype='roadmap',color='bw',source='google',zoom=13)

ggmap(newyork.map)+
  geom_point(data=station.info,aes(x=long,y=lat,color=n.trips),size=3,alpha=0.75)+
  scale_color_gradient(high = 'red',low='lightblue')+
  theme(axis.ticks=element_blank(),axis.text=element_blank())+
  xlab("")+ylab("")


#find the most popular place:

top.station=station.info%>%
        arrange(desc(n.trips))%>%
        head(1)

top.station

busy.station.out =citibike %>% 
                  filter(start.station.id==top.station$start.station.id)%>%
  group_by(end.station.id)%>%
  summarise(n.trips=n(),name=end.station.name[1],
            start.lat=as.numeric(start.station.latitude)[1],
            start.lon=as.numeric(start.station.longitude)[1],
            end.lat=as.numeric(end.station.latitude)[1],
            end.lon=as.numeric(end.station.longitude)[1])%>%
  arrange(desc(n.trips))%>%
  head(20)

# find trips from the most popular place
map_top.station=get_map(location=c(lon=top.station$long,lat=top.station$lat),color='bw',source='google',zoom=14)

ggmap(map_top.station)+
  geom_segment(data=busy.station.out,aes(x=start.lon,y=start.lat,xend=end.lon,yend=end.lat,color=n.trips),
size=1,alpha=0.75)+
  geom_point(data=busy.station.out,aes(x=end.lon,y=end.lat,color=n.trips),size=3,alpha=0.75)+
  geom_point(data=top.station,aes(x=long,y=lat),size=4,alpha=0.5)+
  scale_color_gradient(high='red',low='green')+
  theme(axis.ticks=element_blank(),axis.text=element_blank())+
  xlab("")+ylab("")+
  ggtitle(paste0('Top20 Trips starting at ',top.station$name))
  
```


#### World map:

```{r message = F, warning = F}
ship <- read_csv('data/CLIWOC15.csv')

plot.title = 'Ship Positions by Nationality, 1750-1850'
plot.subtitle = 'Source: Ship Log Books, https://pendientedemigracion.ucm.es/info/cliwoc/'

ggplot() +   
  borders("world", colour="gray50", fill="gray50") +
  geom_point(data = filter(ship, Nationality %in% c('British','Dutch','Spanish','French')),
                           mapping = aes(Lon3,Lat3,color=Nationality), alpha=0.01,size=1) +
  ylim(-75,80)+
  facet_wrap(~Nationality)+
  theme(legend.position="none")+
  ggtitle(bquote(atop(.(plot.title), atop(italic(.(plot.subtitle)), "")))) 

```


#### US MAP

```{r message = F, warning = F}

library(usmap)

#statedonor <- table %>%
  #filter(donor_state %in% statepop$abbr) %>%
  #drop_na(poverty_level) %>%
  #group_by(donor_state) %>%
  #summarise(n=n(),total=sum(donation_total),mean=mean(donation_total))%>%
  #rename(state=donor_state)

plot_usmap(data = statepop, values = "pop_2015", color = "rosybrown1") + 
  scale_fill_continuous(
    low = "white", high = "salmon", name = "population(2015)", label = scales::comma
  ) + theme(legend.position = "right")
```

#### Plotly： A dynamic map. You can put your mouse on the area and get info.

```{r message = F, warning = F}
library(plotly)
df=statepop

df$hover <- with(df, paste0(abbr, '<br>', "population",pop_2015))
                 
# give state boundaries a white border                

l <- list(color = toRGB("white"), width = 2)

# specify some map projection/options

g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

p <- plot_geo(df, locationmode = 'USA-states') %>%
  add_trace(
    z = ~pop_2015, text = ~hover, locations = ~abbr,
    color = ~pop_2015, colors = 'Purples'
  ) %>%
  colorbar(title = "Population") %>%
  layout(
    title = '2011 US Agriculture Exports by State<br>(Hover for breakdown)',
    geo = g
  )
p

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
#chart_link = api_create(p, filename="choropleth-ag")
#chart_link

```
